Other recently published studies in \emph{E.coli} have suggested different models and in some cases have results  and predictions that do not coincide with those presented in this study.
Notably, in \cite{Klumpp2009} a decreased protein concentration for unregulated genes is predicted.
A few differences can explain this seeming discrepancy.
The modeling in \cite{Klumpp2009} relies on data collected under different growth rates than those observed in our work.
The predictions of the model are based on the deduced dependence of various bio-synthesis process rates and physiological properties of the cells on the growth rate, properties that are, in turn, used to calculate the expected protein concentration for unregulated proteins under the different growth rates.
The model in \cite{Klumpp2009} refers to protein concentration and not to protein fraction out of the proteome. These quantities may differ due to changes in the ratio of total protein mass to cell dry weight, or cell volume, as a function of the growth rate.
Thus, this approach is markedly different than the approach we take, which assumes relatively small changes in bio-synthetic rates as a function of growth rate and focuses on the limited bio-synthesis resources as the main driver of changes in the resulting fraction of proteins out of the proteome.
As the model in \cite{Klumpp2009} was only tested against a handful of proteins, it is impossible to decide which of the two models better describes the global effects of growth rate on the proteome composition.